Seismic Time Series Analysis\\Statistics for Spatio-Temporal Data\\\textit{-- project draft --}

### 2020-06-08 project.after.Rmd
complete porting and commenting to project.R

final.training <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.end, force_ms = T)
final.testing <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.final.end, force_ms = T)
final.testing <- window(final.testing, start = c(end(final.training)[1] + 1, 1))
c(chosen.lambda, BoxCox.lambda(final.training))

@@

final.testing.24 <- build_ts(final.testing, periods = c(24))
seasonplot(final.testing.24/sd(final.training.24, na.rm = T), type="l", col=rainbow(7))
legend("topleft", legend=weekdays(seis.test.final.start + (as.difftime(c(0:6), units="days"))), col=rainbow(7), lty=1, cex=0.8)

>>>>

final.training <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.end, force_ms = T)
final.testing <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.final.end, force_ms = T)
final.testing <- window(final.testing, start = c(end(final.training)[1] + 1, 1))
if (!is.null(chosen.lambda)) {
  cat(chosen.lambda, BoxCox.lambda(final.training), chosen.lambda == BoxCox.lambda(final.training), "\n")
}

@@

final.testing.24 <- build_ts(final.testing, periods = c(24))
seasonplot(final.testing.24/sd(final.testing.24, na.rm = T), type="l", col=rainbow(7))
legend("topleft", legend=weekdays(seis.test.final.start + (as.difftime(c(0:6), units="days"))), col=rainbow(7), lty=1, cex=0.8)
